### 2020-06-04 sc20_reviews/response.md

We thank the reviewers for their detailed and insightful feedback.

Changes made in response to reviewer comments:

  * Added Section V-G: Load Imbalance.
  * Added Section V-I: Predicting Strong Scaling with METG.
  * Expanded Section VI: Performance Issues Discovered.
  * Additional changes requested by specific reviewers are described below.

All changes are marked in blue.

@@

  * For a specific example of an application where small task granularities are useful, see <https://ieeexplore.ieee.org/document/8948618>. Figure 2 shows that with a tile size of 1024 the algorithm achieves about 7 TFLOPS/s per GPU. The task executed on each tile is a straightforward matrix multiply, making it easy to determine the the FLOPS (and therefore task granularity): (2\*1024\*1024\*1024/10^9)/7000gflops = 307us.

## Reviewer 2

  * We added Section V-I. This section validates METG against time to solution. We show that it is possible to use METG, along with a single-node measurement of time to solution, to predict the strong scalability of a code (i.e., the point where it reaches 50% parallel efficiency, in terms of both time to solution, and node count). We find that we can predict time to solution (at 50% efficiency) to within a factor of 1.28X on average across 11 programming systems.

  * We expanded Section V-B and V-C to describe how the properties of the various systems influence our results.

@@

  * We expanded Section VI.

## Reviewer 5

  * We agree that cross-validation with mini-apps is a good direction for future work, but that concrete benefits have already been demonstrated in the form of performance bugs found and fixed via Task Bench (see updated Section VI).

  * Whether dependencies are constructed ahead of time or on the fly is a feature of the programming model being used to implement of Task Bench, not a feature of Task Bench itself. E.g., Dask, PaRSEC, Regent and StarPU all construct the task graph on the fly. The core APIs shown in Table 3 are sufficient to do this, it is simply a matter of calling the right programming model APIs for each task. Listing 2 shows how we do this for MPI. All of our implementations are open source and will be linked in the final paper.

### 2020-06-05 5_evaluation.tex
Add table and explanation.

\input{e9_strong}

@@

When we consider all 11 programming systems that scale well enough to
perform this experiment, we find that the average separation between
the ideal and actual intersection points is $1.61\times$ in node count
(max $2.19\times$, min $1.13\times$) and $1.28\times$ in time to
solution (max $1.69\times$, min $1.01\times$).

>>>>

\input{e9_strong}
\input{e11_metg_predict_strong}

@@

Table~\ref{tab:metg-predict-strong} expands this comparison to the 4
patterns tested in Figure~\ref{fig:metg-compute} for all 11
programming systems that scale well enough to evaluate the separation
between the limit-ideal and limit-actual intersections. We see that
overall, the mean separation is less than $2.15\times$ in node count
and less than $1.31\times$ in time to solution, making this an
accurate way to predict strong scaling in 4 patterns we tested in
Section~\ref{subsec:scalability}.

\zap{
When we consider all 11 programming systems that scale well enough to
perform this experiment, we find that the average separation between
the ideal and actual intersection points is $1.61\times$ in node count
(max $2.19\times$, min $1.13\times$) and $1.28\times$ in time to
solution (max $1.69\times$, min $1.01\times$).
}
